Verifying Demonstrations

### 2021-06-17 paper/desired-properties.tex
Cuts desired and security properties sections

We note that, in general terms, protests are petitions with a given time and 
location.
Protests, petitions and elections share that in all three many individuals 
express their opinion.
These opinions can be sensitive (\eg be a cause for discrimination or 
persecution).
For that reason we have strong requirements for verification and privacy for 
elections, it follows that we should have similar properties for protests
and petitions.

@@

%Coercion resistance is not possible to achieve for protests.
Coercion resistance in voting typically relies on physical isolation
(\eg private voting booths), including for digital systems, 
and that is by definition not possible for public events.
For instance, someone could simply physically bring Alice to a protest against her will.
As for receipt freeness, while
desirable \emph{in itself}, it implies a conflict with verifiability in our context:
%appealing at first glance, is not desirable (probably not possible)
%in our context since this will conflict with verifiability:
in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the 
cause of the protest) here implies receipt freeness for \emph{that} the voter voted 
(\ie the protester was there), which would make verifiability impossible.

Therefore in our context, the crucial property is  vote privacy.
More precisely, for the protester we want unlinkability (from the adversary's 
perspective) between a protester's real identity and the participation proof 
(and thus also the protest itself).
Phrased differently, given a participation proof, Grace should not be able to 
distinguish if it was Alice or Bob who participated.
Furthermore, if Grace has managed to link one proof to Alice due to some 
auxiliary knowledge, she should not be able to link it to another proof (from a different protest).

>>>>

We note that, in general terms, protests are petitions with a given time and 
location.
Protests, petitions and elections share that in all three many individuals 
express their opinion.
To support democracy, we need strong requirements for verification and privacy 
for elections, it follows that we should have similar properties for protests
and petitions.

@@

%Coercion resistance is not possible to achieve for protests.
Coercion resistance in voting typically relies on physical isolation
(\eg private voting booths), including for digital systems, and that is by 
definition not possible in our context.
For instance, someone could simply physically bring Alice to a protest against her will.
As for receipt freeness, while
desirable \emph{in itself}, it implies a conflict with verifiability in our context:
%appealing at first glance, is not desirable (probably not possible)
%in our context since this will conflict with verifiability:
in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the 
cause of the protest) here implies receipt freeness for \emph{that} the voter voted 
(\ie the protester was there), which would make verifiability impossible.

Privacy remains as the crucial property.
More precisely, for the protester we want unlinkability (from the adversary's 
perspective) between a protester's real identity and the participation proof 
(and thus also the protest itself).

### 2021-06-17 paper/security-properties.tex
Cuts desired and security properties sections

    \item\label{CountOnce} \emph{Counted only once}:
      A protester can create \emph{one and only one} pseudonym (\(\pid\) in 
      \cref{DefProofShares}) per protest (\(\cid\) in \cref{DefProofShares}), 
      this pseudonym is unique except with negligible probability.
      Analogously, a witness can create \emph{one and only one} pseudonym per 
      protester (\(\wid\) in \cref{DefProofShares}), this pseudonym is unique 
      except with negligible probability.

@@

What these properties say is that pseudonyms must look random 
(\cref{PseudonymUnlink}) and that each psdeudonym must not be reused
more than strictly necessary for the verifiability properties 
(\cref{ProtestUnlink,WitnessUnlink}). In Pfitzmann-Hansen
terminology~\cite{pfitzmann-hansen}, they are role-relationship
pseudonyms, but with increasingly narrowed notions of roles and
relationships (participant of particular protest, witness of a
particular participant at a particular protest).
In the terminology of \textcite{SybilFreePseudonyms}; for each protester a 
protest is a context or identity domain, whereas for each witness every 
protester is a context (or identity domain).

>>>>

    \item\label{CountOnce} \emph{Counted only once}:
      A protester can create \emph{one and only one} pseudonym (\(\pid\) in 
      \cref{DefProofShares}) per protest (\(\cid\) in \cref{DefProofShares}), 
      this pseudonym is unique.

@@

In the terminology of \textcite{SybilFreePseudonyms}; for each protester a 
protest is a context or identity domain, whereas for each witness every 
protester is a context (or identity domain).
